\section{\centerline{EMPLOYMENT}} 
\vspace{0.1in}

{\bf Staff Research Scientist} \hfill Responsible AI Team, Apple, Inc., Cupertino, CA, Oct 2023 - Present
\begin{itemize}
\item Tech lead for red teaming efforts for Apple Intelligence features, including web QA, text summarization, text composition, text assistants and visual generation features.
\item Infrastructure archtect for building large-scale pipelines for automatic red-teaming data synthesization, on-device inference/simulation, and auto grading metric reporting pipelines.
\item Tech lead for developing embedding based semantic override models.
\end{itemize}

{\bf Staff Research Scientist} \hfill Machine Intelligence Sensing Team, Apple, Inc., Cupertino, CA, Jul 2021 - Oct 2023
\begin{itemize}
\item Tech lead for improving handwashing feature for Apple watch. Using audio and motion sensing to improve recall and precisions for handwashing.
\item Tech lead for double tap gesture detection for Apple watch, featured in \href{https://www.youtube.com/live/ZiP1l7jlIIA?si=91y1iFq4ch-ziGd4&t=763}{Sep 2023 Apple special event}.
\item On-device audio detection model for health event for Airpods.
\item Location tracking and prediction algorithm based on IMU sensing to optimize energy and battery for Vision Pro.
\end{itemize}

{\bf Founding Member} \hfill Dawnlight, Inc., Palo Alto, CA, Jan 2019 - Jul 2021
\begin{itemize}
\item Design and develop end-to-end data collection, signal processing, model training and serving architecture (in C++/C) on various IoT edge devices for healthcare related audio event detection.
\item Design and develop state-of-the-art audio event detection model (benchmarked on multiple public datasets).
\item Design and develop end-to-end data processing, model training and serving architecture for Clincal Decision Support System (CDSS).
\item Design and develop end-to-end data processing, model training and feature demo on activity recognition using radar signals and RFID signals.
\item Working with a team to design and develop a generic end-to-end machine learning platform with hyper-parameter tuning (using Ray) and container orchestration pipeline support.
\item Working with a team to develop and maintain full-stack daily operations, including flask services, bluetooth services, docker containers, Kafka, gRPC, etc.
\end{itemize}

{\bf Senior Research Scientist} \hfill Microsoft, Sunnyvale, CA, Aug 2016 - Jan 2019
\begin{itemize}
  %  \item Research and development language model and domain adaptation pipeline for enterprise speech recognition system.
\item Language model personalization using topic models, context matching and style filtering.
\item Design and develop end-to-end data processing, model training and adaptation evaluation pipeline.
\item Language model adaptation support for Microsoft Teams product for both meeting and broadcasting scenarios. Prototype demo'ed at Microsoft \href{https://medius.studios.ms/Embed/Video/BRK2403?sid=BRK2403}{\emph{\underline{Build 2018}}}, \href{https://myinspire.microsoft.com/videos/87f6a740-cf4c-4f45-a405-f62f1a28740a}{\emph{\underline{Inspire 2018}}}, and \href{https://myignite.techcommunity.microsoft.com/sessions/66676}{\emph{\underline{Ignite 2018}}}.
\end{itemize}

{\bf Research Scientist} \hfill Yahoo! Labs, Sunnyvale, CA, Feb 2015 - Aug 2016
\begin{itemize}
  % \item Research on query understanding and sequence tagging for online Ads serving system.
  % \item Research on query classification and user intent prediction for mobile search product.
\item Develop query understanding and sequence tagging models for online Ads serving system.
\item Design and develop query classification and user intent prediction pipeline for mobile search.
\item Research, design and develop on ``Chat Bot as a Service'' platform.
\end{itemize}

{\bf Graduate Research Assistant} \hfill Department of Computer Science,
University of Maryland, College Park, MD, Sep 2010 - Jun 2014
\begin{itemize}
\item Academic Advisor: Jordan Boyd-Graber
\item Research Interest: Machine Learning, Non-parametric Bayesian Learning, Cloud Computing
\item Design and implement online variational inference for adaptor grammars.
\item Design and implement online variational inference for topic models with infinite vocabulary.
\item Design and implement variational inference for latent Dirichlet allocation in MapReduce.
\item Design and implement variational inference for Indian buffet process in MapReduce.
  % \item Enable variational inference for synthetic topic modelling system in MapReduce.
\end{itemize}

{\bf Research Intern} \hfill Yahoo! Labs, New York City, NY, Jun 2014 - Aug 2014
\begin{itemize}
\item Large scale unsupervised nonparametric models for user behavior analysis.
\end{itemize}

{\bf Research Intern} \hfill Microsoft Research, Redmond, WA, May 2013 - Aug 2013
\begin{itemize}
\item Mentor: Jason D. Williams
\item Design and implement three models in discovering latent structure in dialogues.
\item Achieve comparably well results against many other models on real datasets.
\end{itemize}

{\bf Software Engineering Intern} \hfill comScore, Inc., Reston, VA, May 2010 - Aug 2010
\begin{itemize}
\item Implement data transfer and formatter block for new deployed Hadoop distributed file system.
\item Research and develop cookie deletion and prediction system for comScore.
\end{itemize}

%% {\bf Graduate Teaching Assistant} \hfill Department of Computer Science, University of Maryland, College Park, MD, Sep 2009 - May 2010
%% \begin{itemize}
%% \item CMSC 131: Object-Oriented Programming I, Fall 2009.
%% \item CMSC 422: Introduction to Artificial Intelligence, Spring 2010.
%% \end{itemize}

%% {\bf Software Engineering Industrial Attachment} \hfill StarHub, Inc., Singapore, Jan 2008 - Jun 2008
%% \begin{itemize}
%% \item Study on customer service system and client feedback process.
%% \item Develop data collection and analysing software for Customer Service.
%% \item Develop high-efficiency data processing system.
%% \item Database development and administration.
%% \item Design and develop reliable database system in MySQL for Customer Service.
%% \item Automate data processing and analysing system with Microsoft Office and VBA.
%% \end{itemize}
