% LaTeX resume using res.cls
\documentclass{style/resume}
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{times}

\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Ke Zhai} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{Ke Zhai}
\address{
  % 3405 Tulane Dr., Apt. 24, Hyattsville, Maryland 20783\\
  Tel no.: (240) 460-9082\\
  zhaikedavy@gmail.com
}

\begin{resume}
  \vspace{0.1in}
  % \moveleft.5\sectionwidth\centerline{Objective: Position as technical writer or editor.}  

  \section{EDUCATION}
  \vspace{0.1in}

  Ph.D. in Computer Science, Department of Computer Science\\
  {\bf University of Maryland, College Park, MD, 2014}\\
  GPA: 3.9/4.0. Supervisor: Jordan Boyd-Graber and Jimmy Lin (co-supervied)\\
  Research topic: Large Scale Inference for Probabilistic Bayesian Models

  M.S. in Computer Science, Department of Computer Science\\
  {\bf University of Maryland, College Park, MD, 2011}\\
  GPA: 3.9/4.0. Supervisor: Jordan Boyd-Graber and Jimmy Lin (co-supervied)\\
  Research topic: Variational Bayesian Inference of Latent Dirichlet Allocation in MapReduce\\
  Master scholary paper: Using Variational Inference and MapReduce to Scale Topic Modeling

  B.Eng. in Computer Engineering with first class honor, School of Computer Engineering\\
  {\bf Nanyang Technological University, Singapore, 2009}\\
  GPA: 4.65/5.0. Supervisor: Wee Keong Ng\\
  Research topic: Privacy-Preserving Data Mining\\
  Undergraduate thesis: An Embedded Caching Framework for Privacy-Preserving Data Mining

  \section{EMPLOYMENT} 
  \vspace{0.1in}
  {\bf Research Scientist,} Yahoo! Labs, Sunnyvale, CA, Feb 2015 - present
  \begin{itemize}
  \item Research on query understanding and sequence tagging for
    online Ads serving system.
  \item Research on query classification and user intent prediction
    for mobile search product.
  \end{itemize}

  {\bf Graduate Research Assistant,} Department of Computer Science,
  University of Maryland, College Park, MD, Sep 2010 - Jun 2014
  \begin{itemize}
  \item Academic Advisor: Jordan Boyd-Graber
  \item Research Interest: Machine Learning, Non-parametric Bayesian
    Learning, Cloud Computing
  \item Design and implement online variational inference for adaptor grammars.
  \item Design and implement online variational inference for topic models with infinite vocabulary.
  \item Design and implement variational inference for latent Dirichlet allocation in MapReduce.
  \item Design and implement variational inference for Indian buffet process in MapReduce.
    % \item Enable variational inference for synthetic topic modelling system in MapReduce.
  \end{itemize}

  {\bf Research Intern} Yahoo! Labs, New York City, NY, Jun 2014 - Aug 2014
  \begin{itemize}
  \item Large scale unsupervised nonparametric models for user behavior analysis.
  \end{itemize}

  {\bf Research Intern} Microsoft Research, Redmond, WA, May 2013 - Aug 2013
  \begin{itemize}
  \item Mentor: Jason D. Williams
  \item Design and implement three models in discovering latent structure in dialogues.
  \item Achieve comparably well results against many other models on real datasets.
  \end{itemize}

  {\bf Software Engineering Intern,} comScore, Inc., Reston, VA, May 2010 - Aug 2010
  \begin{itemize}
  \item Implement data transfer and formatter block for new deployed Hadoop distributed file system.
  \item Research and develop cookie deletion and prediction system for comScore.
  \end{itemize}

  {\bf Graduate Teaching Assistant,} Department of Computer Science, University of Maryland, College Park, MD, Sep 2009 - May 2010
  \begin{itemize}
  \item CMSC 131: Object-Oriented Programming I, Fall 2009.
  \item CMSC 422: Introduction to Artificial Intelligence, Spring 2010.
  \end{itemize}
  
  {\bf Software Engineering Industrial Attachment,} StarHub, Inc., Singapore, Jan 2008 - Jun 2008
  \begin{itemize}
  \item Study on customer service system and client feedback process.
  \item Develop data collection and analysing software for Customer Service.
  \item Develop high-efficiency data processing system.
  \item Database development and administration.
  \item Design and develop reliable database system in MySQL for Customer Service.
  \item Automate data processing and analysing system with Microsoft Office and VBA.
  \end{itemize}
  
  \section{PUBLICATIONS (* indicates equal contributor)} 
  \vspace{0.1in}

  {\bf Ke Zhai}, Yuening Hu, Hua Ouyang and Zornitsa
  Kozareva. ``Dropout with Probabilistic Priors''. {\it Annual Meeting
    of the Association for Computational Linguistics} (ACL), under
  review.

  Weiwei Guo, Qi Li, {\bf Ke Zhai}, and Zornitsa Kozareva. ``Entity
  Linking for Domain-Specific Queries without Mention
  Annotation''. {\it Annual Meeting of the Association for
    Computational Linguistics} (ACL), under review.

  {\bf Ke Zhai}, Zornitsa Kozareva, Yuening Hu, Qi Li and Weiwei
  Guo. ``Query to Knowledge: Unsupervised Entity Extraction from
  Shopping Queries using Adaptor Grammars''. {\it Special Interest
    Group on Information Retrieval} (SIGIR), under review.

  {\bf Ke Zhai}, Yuening Hu and Jianhui Chen. ``Logistic Normal Topic
  Models via Hessian-free Optimization''. {\it International
    Conference on Machine Learning} (ICML), under review.

  {\bf Ke Zhai}, Jordan Boyd-Graber and Shay B. Cohen. ``Online
  Adaptor Grammars with Hybrid Inference''. {\it Transaction of the Association
    for Computational Linguistics} (TACL), Oct 2014.

  {\bf Ke Zhai}, and Jason D. Williams. ``Discovering Latent Structure
  in Task-Oriented Dialogues''. {\it Annual Meeting of the Association
    for Computational Linguistics} (ACL), Jun 2014.

  {\bf Ke Zhai}*, Yuening Hu*, Vladimir Edelman, and Jordan
  Boyd-Graber. ``Polylingual Tree-Based Topic Models for Translation
  Domain Adaptation''. {\it Annual Meeting of the Association for
    Computational Linguistics} (ACL), Jun 2014.

  {\bf Ke Zhai}, and Jordan Boyd-Graber. ``Online Latent Dirichlet
  Allocation with Infinite Vocabulary''. {\it Internation Conference
    on Machine Learning} (ICML), Jun 2013.

  {\bf Ke Zhai}*, Yuening Hu*, Jordan Boyd-Graber, and Sinead
  Williamson. ``Modeling Images using Transformed Indian Buffet
  Processes''. {\it Internation Conference on Machine Learning}
  (ICML), Jun 2012.

  {\bf Ke Zhai}, Jordan Boyd-Graber, Nima Asadi, and Mohamad
  Alkhouja. ``Mr. LDA: A Flexible Large Scale Topic Modeling Package
  using Variational Inference in MapReduce''. {\it ACM Internation
    Conference on World Wide Web} (WWW), Apr 2012.

  {\bf Ke Zhai}, Wee Keong Ng, Andre Ricardo Herianto and Shuguo
  Han. ``Speeding Up Secure Computations via Embedded Caching''. {\it
    Proceedings of SIAM International Conference on Data Mining}
  (SDM), Apr 2009.

  \section{PROFESSIONAL CONTRIBUTION}
  \vspace{0.1in}
  Activate contributor for MapReduce library Cloud$^9$ and Hadoop toolkit Ivory.\\
  Online released code-base on GitHub, https://github.com/kzhai.
  \begin{itemize}
  \item MapReduce latent Dirichlet allocation (Variational Beyesian
    inference, with extension to informed prior and polylingual LDA).
    \begin{quotation}
      % The second comes out of the Cloud Computing Research Team based in the University of Maryland and is named Mr. LDA. \ldots 
      ``I tried both and found that, despite \emph{Mr. LDA}'s cringeworthy name, it's much faster than \emph{Mahout}'s implementation so decided to go with that one.''\\
      \vspace{1mm}
      \hfill --- \textbf{Kris Jack}, BSc Hons, Ph.D., Chief Data Scientist, Mendeley
    \end{quotation}
  \item Latent Dirichlet allocation (Gibbs sampling, variational Bayesian inference and online version).
  \item Non-parametric Bayesian models (Indian buffet process, hierarchical Dirichlet process and infinite Gaussian mixture model).
  \end{itemize}

  \section{PROFESSIONAL SKILLS}
  \vspace{0.1in}
  Java, Python, Matlab, MapReduce, Hadoop, Spark, SQL, C++/C, VBA\\
  Linux, Windows, Mac OS X\\
  Microsoft Office, Eclipse, NetBeans, Emacs, Photoshop

\end{resume}
\end{document}
