\section{\centerline{PUBLICATION (* indicates equal contributor)}}
\vspace{0.1in}

{\bf Ke Zhai}*, and Huan Wang*. ``Adaptive Dropout with Rademacher Complexity Regularization''. {\it International Conference on Learning Representations} (ICLR), May 2018.

{\bf Ke Zhai}, Zornitsa Kozareva, Yuening Hu, Qi Li and Weiwei Guo. ``Query to Knowledge: Unsupervised Entity Extraction from Shopping Queries using Adaptor Grammars''. {\it International ACM SIGIR Conference on Research and Development in Information Retrieval} (SIGIR), Jul 2016.

Zornitsa Kozareva, Qi Li, {\bf Ke Zhai} and Weiwei Guo. ``Recognizing Salient Entities in Shopping Queries''. {\it Annual Meeting of the Association for Computational Linguistics} (ACL), Jun 2016.

{\bf Ke Zhai}, Jordan Boyd-Graber and Shay B. Cohen. ``Online Adaptor Grammars with Hybrid Inference''. {\it Transaction of the Association for Computational Linguistics} (TACL), Oct 2014.

{\bf Ke Zhai}, and Jason D. Williams. ``Discovering Latent Structure in Task-Oriented Dialogues''. {\it Annual Meeting of the Association for Computational Linguistics} (ACL), Jun 2014.

{\bf Ke Zhai}*, Yuening Hu*, Vladimir Edelman, and Jordan Boyd-Graber. ``Polylingual Tree-Based Topic Models for Translation Domain Adaptation''. {\it Annual Meeting of the Association for Computational Linguistics} (ACL), Jun 2014.

{\bf Ke Zhai}, and Jordan Boyd-Graber. ``Online Latent Dirichlet Allocation with Infinite Vocabulary''. {\it International Conference on Machine Learning} (ICML), Jun 2013.

{\bf Ke Zhai}*, Yuening Hu*, Jordan Boyd-Graber, and Sinead Williamson. ``Modeling Images using Transformed Indian Buffet Processes''. {\it International Conference on Machine Learning} (ICML), Jun 2012.

{\bf Ke Zhai}, Jordan Boyd-Graber, Nima Asadi, and Mohamad Alkhouja. ``Mr. LDA: A Flexible Large Scale Topic Modeling Package using Variational Inference in MapReduce''. {\it ACM International Conference on World Wide Web} (WWW), Apr 2012.

{\bf Ke Zhai}, Wee Keong Ng, Andre Ricardo Herianto and Shuguo Han. ``Speeding Up Secure Computations via Embedded Caching''. {\it Proceedings of SIAM International Conference on Data Mining} (SDM), Apr 2009.
